{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-02-18 documents/lessons_learned.tex
More progress on summary

Rather than focus effort on making marginal improvements to avoid errors in a certain technique, it may be better to find an experimental technique that is totally immune to these problems. Obviously this isn't always possible or practical.

>>>>

This was written in 4 parts: first, rough lab notes were made, then this was cleaned up into a long thesis-like document, and then this was compressed into the final paper. However, in that final compression step, a lot of "texture" and pedagogy was lost.

Rather than focus effort on making marginal improvements to avoid errors in a certain technique, it may be better to put more effort to find a better experimental technique that is totally immune to these problems. Obviously this isn't always possible or practical.

### 2021-02-18 documents/summary.tex
More progress on summary

Whether the small difference in driven amplitude between, for example, a $Q\approx0.5$ host structure normal mode and a $	Q\lessapprox6$ virion mode could possibly be of any clinical value is unknown to us.

@@

In our cursory testing, Bacteriophage T4 did not appear to be lysed by microsecond pulses between 6 and 12 GHz at about 70 V/m, nor, exploring non-resonant inactivation, did nanosecond pulses up to 1 MV/m appear to have any effect. Note than neither of these regimes overlap with the results of the previous studies.

@@

Electrorotation\cite{Electrorotation1988}\cite{Electrorotation1997} of viruses has been reported\cite{Analysis2004}\cite{New1999}\cite{comprehensive2001}, but as yet only in a non-destructive low-speed sub-synchronous regime for sensing, using optical means to detect rotation rate. Dielectrophoresis and electrostatic trapping of viruses has also been reported.

Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or perhaps directly via extraction from CryoEM maps.

Tsen

@@

Thermal effects appear to be most common. Most critically, the localized hotspots created by microwave exposure are often almost impossible to measure. Ideally, experimental design should guarantee that even slight localized temperature rise, any more than about 3 C, cannot occur \cite{DNA2004}, or use thermally-matched shams.

FDTD simulation of exposure geometry and sample heating is now usually possible with free, open-source software\footnote{PyTorch FDTD library from \cite{Highly2019} was used in our study with some modification, but \cite{CUDAbased2019} and \cite{openEMS} are also excellent} and should be performed. Metal ions from electrodes, UV exposure, and polymer surface effects must be ruled out by experimental design. The only artifact-free appear to be 1. Remote exposure, actively cooled OR pulsed exposure with sufficiently short pulses to rule out heating, with.

Coherent control targeting small proteins seems to require very large fields. Coherent control of large-scale structural modes using ; however these results have failed replication.

@@

Although not sensitive to infectivity, as suggested by \cite{Quantification2020}, amplification-free fluorescence dsDNA detection using photon-counting plate readers using a 1:1 mix of viral solution with 1/4000 Biotium GelGreen (a safe Acridine Orange (N-alkylacridinium) based flurophore) is a very convenient (stable over long periods of time, requires no host culture) and sufficiently sensitive (titers down to $10^8$ of T4 (170 kbp dsDNA)) assay both for capsid damage and, by melting the capsid with an autoclave, for general virus titer estimation, far faster than even high-throughput plaque assays. More useful enveloped viral surrogates like Pseudomonas phage Phi 6 are RNA and a lower sensitivity can be expected.

@@

ImageJ

In both of our final experimental setups, non-grounded, single-sided coplanar waveguides were used as exposure chambers, inspired by \cite{Microwave2007}. A programmable syringe pumped 50 uL of fluid at a constant rate through one of the coplanar channels. Simulations showed a significant decrease in field. \cite{Microchamber2011} and \cite{Characterization2012} provide a good review of pulse exposure cells and a design which is much better than ours and should be used instead. Such cells should be used rather than our crude design. \footnote{the utility wcalc was used extensively}.

Avalanche transistors are sufficient and perhaps the easiest way to produce high power sub 100 ps pulses. We stole an avalanche Marx design verbatim from Li (\cite{Development2016b} \cite{Design2018c}), which allows large pulses from lower voltage supplies (albeit requiring somewhat costly capacitors); but  If a fast laser is available, Auston switches appear to be equally effective. It is difficult to make spark gaps run than 200 ps without the Marx overvoltage.

We are particularly excited by the prospect of using picosecond time-domain measurements not only to perform steady state dielectric measurements or monitor the input pulse, as is now common practice, but to resolve the internal effects of a single high-voltage pulse on the virus in real time - a technique which has not, to our knowledge, previously been demonstrated. Scan-converter based transient digitizers, such as the Tektronix SCD-5000 series, appear to be the lowest-cost method of obtaining such THz sampling bandwidths. When high voltage pulses are available, miniaturized \ntilde 2 mm internal diameter continuously pumped scan converter tubes like Fecher micro-oscillographs using in-vacuum CMOS image sensors for direct-electron-detection appear to be an easy way to digitize 20+ GHz transients. The main bandwidth limitation appears to be the length of the Y deflection plate and the sensitivity of the recording medium.

>>>>

However, whether the small difference in driven amplitude between, for example, a $Q\approx0.5$ host structure normal mode and a $Q\lessapprox6$ virion mode could possibly be of any clinical value is unknown to us.

@@

In our cursory testing, Bacteriophage T4 did not appear to be lysed by microsecond pulses between 6 and 12 GHz at about 70 V/m, nor, exploring non-resonant inactivation, did nanosecond pulses up to 1 MV/m appear to have any effect. Note that neither of these regimes overlap with the results of the previous studies.

@@

Electrorotation\cite{Electrorotation1988}\cite{Electrorotation1997} of viruses has been reported\cite{Analysis2004}\cite{New1999}\cite{comprehensive2001}, but as yet only in a non-destructive low-speed sub-synchronous regime for sensing, using optical means to detect rotation. Dielectrophoresis and electrostatic trapping of viruses has also been reported.

Data on the charge distribution of the virion can be obtained by and 2D-PAGE relative protein composition or, interestingly, perhaps directly via extraction from CryoEM maps.

@@

Thermal effects appear to be most common. Most critically, the localized hotspots created by microwave exposure are often almost impossible to measure. Ideally, experimental design should guarantee that even slight localized temperature rise, any more than about 3 C, cannot occur \cite{Sharp1983}\cite{DNA2004}, or use thermally-matched shams\cite{Basic1983}. \cite{Effects1951}

FDTD simulation of exposure geometry and sample heating is now usually possible with free, open-source software\footnote{PyTorch FDTD library from \cite{Highly2019} was used in our study with some modification, but \cite{CUDAbased2019} and \cite{openEMS} are also excellent} and should be performed. As above, metal ions from electrodes, UV exposure, and polymer surface effects\cite{Effect1994a} must be ruled out by experimental design. The only artifact-free appear to be 1. Remote exposure, actively cooled OR pulsed exposure with sufficiently short pulses to rule out heating, with.

 There is a body of work on coherent control of viral inactivation using picosecond laser exposure \cite{Maximum2010}; targeting small proteins seems to require very large fields\cite{Picosecond2016b}, but driving using Raman scattering \cite{Inactivation2007} \cite{Prospects2012}\cite{Studies2014} and molecular dynamics \cite{Maximum2010} (but without considering heat-bath damping). however these results have failed replication\cite{No2011}. Interestingly, if the well-established 1 TW power density\cite{Targeted2002} for mammalian cell laser damage is scaled linearly with time to the nanosecond regime ($1\ \text{TW/m}^2 / (100\ \text{ps} / 0.3\ \text{ps}) = 3\ \text{GW/m}^2$),

@@

Although not sensitive to changes in infectivity, as suggested by \cite{Quantification2020}, amplification-free fluorescence dsDNA detection using photon-counting plate readers using a 1:1 mix of viral solution with 1/4000 Biotium GelGreen (a safe Acridine Orange (N-alkylacridinium) based flurophore) is a very convenient (stable over long periods of time, requires no host culture) and sufficiently sensitive (titers down to $10^8$ of T4 (170 kbp dsDNA)) assay both for capsid damage and, by melting the capsid with an autoclave, for general virus titer estimation, far faster than even high-throughput plaque assays. More useful enveloped viral surrogates like Pseudomonas phage Phi 6 are RNA and a lower sensitivity can be expected.

@@

If CCD sensors with a, ImageJ \cite{Image2012} A silicon photomultiplier may be sufficient in some cases.

However, these initial tests were marred by use of a domestic fridge to store phage, which unexpectedly froze regularly overnight, apparently reducing phage titer, along with our accidental use of T4r+, which is not an "improved" T4r, as we believed, but rather a mutation away from rapid-lysis, meaning that the lysis behavior is far slower (see \cite{Spontaneous1946}) and, in our testing, lysis of T4r+ only occurred on plaque assay plates (where culture growth and log stage infectivity is maintained for many days).

Nephelometry (right-angle light scattering measurement) and turbidimetric (transmission) using CdS and LtoF sensors; despite being visible to the naked eye "clean" 2 hour E. coli cultures do not .  Turbidimetry Impedimietric In addition, removing the necessitating 
$\beta$-galactosidase luciferase Promega Beta-Glo\cite{rapid2014}. While undoubtedly useful for quantifying $\beta$-galactosidase, because of ambiguities in the rise and decay of the luminescence signal, short shelf life when components are mixed, storage and reagent mixing requirements, and relatively high cost, Beta-Glo assaying compared unfavorably to direct fluorescence for this application, but this may have been user error.

It is difficult to make spark gaps run faster than 200 ps without high-pressure or Marx overvoltage. Avalanche transistors appear to be the easiest way to produce high power sub 100 picosecond pulses. We stole an avalanche Marx design verbatim from Li (\cite{Development2016b} \cite{Design2018c}), which allows large pulses from safer lower voltage supplies (albeit requiring somewhat costly capacitors); but

In both of our final experimental setups, non-grounded, single-sided coplanar waveguides were used as exposure chambers, inspired by \cite{Microwave2007}. A programmable syringe pumped 50 uL of fluid at a constant rate through one of the coplanar channels. Simulations showed a significant decrease in field. \cite{Microchamber2011} and \cite{Characterization2012} provide a good review of pulse exposure cells and a design which is much better than ours and should be used instead. Such cells should be used rather than our crude design. \footnote{The utility wcalc was used extensively}.

If a fast laser is available, Auston switches appear to be equally effective.

We are particularly excited by the prospect of using picosecond time-domain measurements not only to perform steady state dielectric measurements or monitor the input pulse, as is now common practice, but to resolve the internal effects of a single high-voltage pulse on the virus in real time. Scan-converter based transient digitizers, such as the Tektronix SCD-5000 series, appear to be the lowest-cost method of obtaining such THz sampling bandwidths. When high voltage pulses are available, miniaturized \ntilde 2 mm internal diameter continuously pumped scan converter tubes like Fecher micro-oscillographs using in-vacuum CMOS image sensors for direct-electron-detection appear to be an easy way to digitize 20+ GHz transients. The main bandwidth limitation appears to be the length of the Y deflection plate and the sensitivity of the recording medium.
